A word-sense representation for documents based on information value and word sense disambiguation

### 2014-03-19 paper/refactor.tex

\section{Conclussion \& Future work}
The original scope of this investigation was the definition of a measure of distance between the works of a whole year and a concept; so we could measure whether the literary production of Lenin in some year was close to ``revolution'', ``theory'', etc.  With this purpose, we defined the \textbf{top senses} of a text, and measured the distance between them and other senses in a topological way.

>>>>

\section{Conclussion \& Future work}

The original scope of this investigation was the definition of a measure of distance between the works of a whole year and a concept; so we could measure whether the literary production of Lenin in some year was close to ``revolution'', ``theory'', etc.  With this purpose, we defined the \textbf{top senses} of a text, and measured the distance between them and other senses in a topological way.

Although the final results were not the expected, some tools we developed in our way proved to be promising. The hybrid method for extracting top senses of the text based in entropy analisis plus sense disambiguation worked in an acceptable fashion, with lot of room for improvement by using better WSD algorithms. In the other hand, the topological representation of a text as a set of senses has yet to experimented with better semantic similarity functions than the one used here.
